---
title: "SRI 2017- Urban Forests"
author: "Kaden Loring"
date: "6/7/2017"
output:
  word_document: default
  pdf_document: default
  html_document: default
---
####Forest Observations

Measurements of several variables were taken in and around the urban forest on Saint Thomas University campus over multiple days and weather conditions. The Forest was divided into a 4 x 7 grid of 28 regions. During every measurement, three measurements were taken at random positions within each region. All measurements taken for each region were then averaged and plotted as thematic choropleth maps to compare microclimate variances throughout the defined area of the forest and its adjacent area. 

####Required Packages

```{r}
suppressMessages(library(tidyverse))
suppressMessages(library(dplyr))
suppressMessages(library(ggplot2))
suppressMessages(library(ggmap))
suppressMessages(library(EBImage))
suppressMessages(library(knitr))
```

####Define Plot Functions
```{r}
#define common plot background aesthetic
commonplot <- theme(plot.background = element_rect(fill="snow"),
        panel.background = element_rect(fill="white"))
```

#####Saint Thomas University Urban Forest

```{r message= FALSE}
#map of forest and surrounding area
Forest2 <- get_map(location= c(Lon= -80.257248, Lat= 25.924042), zoom = 17, maptype = "satellite")

Forestmap2 <- ggmap(Forest2, extent= "device")

Forestmap2
```

###Setup

Required Setup

```{r message= FALSE}
#read csv with Forest measurements Data
SM <- read.csv("~/Documents/SRI_17/SoilMoisture/Spreadsheets/SM_Official_Spreadsheet.csv")

#Set Region numbers as factors for grouping
SM$Region <- as.factor(SM$Region)

  #SM$Region (run for reference)

#remove rows with NA or blank measurements by Lat variable
SM <- SM[!(is.na(SM$Lat) | SM$Lat==""), ]

#Data Frame containing average VWC per Region ID
#group by region and compute average VWC
VWCRegionAv <- aggregate(SM$VWC,by=list(SM$Region),FUN=mean)

  #VWCRegionAv (Run for Reference)

#Spatial Polygon Data Frame- Creation
suppressMessages(library(sp))
suppressMessages(library(plyr))


#Define single "polygon"s
Region1 <- Polygon(rbind(c(-80.259960, 25.925354), c( -80.259209, 25.925354), c(-80.259209, 25.924808), c(-80.259960, 25.924808)))

Region2 <- Polygon(rbind(c(-80.259960, 25.924808), c(-80.259209, 25.924808), c(-80.259209, 25.924262), c( -80.259960, 25.924262)))     

Region3 <- Polygon(rbind(c(-80.259960, 25.924262), c(-80.259209, 25.924262), c(-80.259209, 25.923716), c(-80.259960, 25.923716)))

Region4 <- Polygon(rbind(c(-80.259960, 25.923716), c(-80.259209, 25.923716), c(-80.259209, 25.923170), c(-80.259960, 25.923170)))

Region5 <- Polygon(rbind(c(-80.259209, 25.925354), c(-80.258458, 25.925354), c( -80.258458, 25.924808), c( -80.259209, 25.924808)))

Region6 <- Polygon(rbind(c(-80.259209, 25.924808), c(-80.258458, 25.924808), c(-80.258458, 25.924262), c(-80.259209, 25.924262)))

Region7 <- Polygon(rbind(c(-80.259209, 25.924262), c(-80.258458, 25.924262), c(-80.258458, 25.923716), c(-80.259209, 25.923716)))

Region8 <- Polygon(rbind(c(-80.259209, 25.923716), c(-80.258458, 25.923716), c(-80.258458, 25.923170), c(-80.259209, 25.923170)))

Region9 <- Polygon(rbind(c(-80.258458, 25.925354), c(-80.257707, 25.925354), c(-80.257707, 25.924808), c(-80.258458, 25.924808)))  

Region10 <- Polygon(rbind(c(-80.258458, 25.924808), c(-80.257707, 25.924808), c(-80.257707, 25.924262), c(-80.258458, 25.924262)))  

Region11 <- Polygon(rbind(c(-80.258458, 25.924262), c(-80.257707, 25.924262), c(-80.257707, 25.923716), c(-80.258458, 25.923716)))  

Region12 <- Polygon(rbind(c(-80.258458, 25.923716), c(-80.257707, 25.923716), c(-80.257707, 25.923170), c(-80.258458, 25.923170)))

Region13 <- Polygon(rbind(c(-80.257707, 25.925354), c(-80.256956, 25.925354), c(-80.256956, 25.924808), c(-80.257707, 25.924808)))

Region14 <- Polygon(rbind(c(-80.257707, 25.924808), c(-80.256956, 25.924808), c(-80.256956, 25.924262), c(-80.257707, 25.924262)))

Region15 <- Polygon(rbind(c(-80.257707, 25.924262), c(-80.256956, 25.924262), c(-80.256956, 25.923716), c(-80.257707, 25.923716)))

Region16 <- Polygon(rbind(c(-80.257707, 25.923716), c(-80.256956, 25.923716), c(-80.256956, 25.923170), c(-80.257707, 25.923170)))

Region17 <- Polygon(rbind(c(-80.256956, 25.925354), c(-80.256205, 25.925354), c(-80.256205, 25.924808), c(-80.256956, 25.924808)))

Region18 <- Polygon(rbind(c(-80.256956, 25.924808), c(-80.256205, 25.924808), c(-80.256205, 25.924262), c(-80.256956, 25.924262)))

Region19 <- Polygon(rbind(c(-80.256956, 25.924262), c(-80.256205, 25.924262), c(-80.256205, 25.923716), c(-80.256956, 25.923716)))

Region20 <- Polygon(rbind(c(-80.256956, 25.923716), c(-80.256205, 25.923716), c(-80.256205, 25.923170), c(-80.256956, 25.923170)))

Region21 <- Polygon(rbind(c(-80.256205, 25.925354), c(-80.255454, 25.925354), c(-80.255454, 25.924808), c(-80.256205, 25.924808)))

Region22 <- Polygon(rbind(c(-80.256205, 25.924808), c(-80.255454, 25.924808), c(-80.255454, 25.924262), c(-80.256205, 25.924262)))

Region23 <- Polygon(rbind(c(-80.256205, 25.924262), c(-80.255454, 25.924262), c(-80.255454, 25.923716), c(-80.256205, 25.923716)))

Region24 <- Polygon(rbind(c(-80.256205, 25.923716), c(-80.255454, 25.923716), c(-80.255454, 25.923170), c(-80.256205, 25.923170)))

Region25 <- Polygon(rbind(c(-80.255454, 25.925354), c(-80.254703, 25.925354), c(-80.254703, 25.924808), c(-80.255454, 25.924808)))

Region26 <- Polygon(rbind(c(-80.255454, 25.924808), c(-80.254703, 25.924808), c(-80.254703, 25.924262), c(-80.255454, 25.924262)))

Region27 <- Polygon(rbind(c(-80.255454, 25.924262), c(-80.254703, 25.924262), c(-80.254703, 25.923716), c(-80.255454, 25.923716)))

Region28 <- Polygon(rbind(c(-80.255454, 25.923716), c(-80.254703, 25.923716), c(-80.254703, 25.923170), c(-80.255454, 25.923170)))

#Turn into polygons (plural) region (combines them)
#[Ex. (Regionwhole <- Polygons(list(Region1, Region2, Region3, Region4, Region5, Region6, Region7, Region8, Region9)))]
Region1 <- Polygons(list(Region1), "1")

Region2 <- Polygons(list(Region2), "2")

Region3 <- Polygons(list(Region3), "3")

Region4 <- Polygons(list(Region4), "4")

Region5 <- Polygons(list(Region5), "5")

Region6 <- Polygons(list(Region6), "6")

Region7 <- Polygons(list(Region7), "7")

Region8 <- Polygons(list(Region8), "8")

Region9 <- Polygons(list(Region9), "9")

Region10 <- Polygons(list(Region10), "10")

Region11 <- Polygons(list(Region11), "11")

Region12 <- Polygons(list(Region12), "12")

Region13 <- Polygons(list(Region13), "13")

Region14 <- Polygons(list(Region14), "14")

Region15 <- Polygons(list(Region15), "15")

Region16 <- Polygons(list(Region16), "16")

Region17 <- Polygons(list(Region17), "17")

Region18 <- Polygons(list(Region18), "18")

Region19 <- Polygons(list(Region19), "19")

Region20 <- Polygons(list(Region20), "20")

Region21 <- Polygons(list(Region21), "21")

Region22 <- Polygons(list(Region22), "22")

Region23 <- Polygons(list(Region23), "23")

Region24 <- Polygons(list(Region24), "24")

Region25 <- Polygons(list(Region25), "25")

Region26 <- Polygons(list(Region26), "26")

Region27 <- Polygons(list(Region27), "27")

Region28 <- Polygons(list(Region28), "28")

#make into a SpatialPolygons object 
#(requires 'Polygons' type arguments (*notice plurality of Polygons))
map <- SpatialPolygons(list(Region1, Region2, Region3, Region4, Region5, Region6, Region7, Region8, Region9, Region10, Region11, Region12, Region13, Region14, Region15, Region16, Region17, Region18, Region19, Region20, Region21, Region22, Region23, Region24, Region25, Region26, Region27, Region28), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

#makes Spatial Polygons Data Frame with VWCRegionAv as Data
map <- SpatialPolygonsDataFrame(map, VWCRegionAv)

#ensure class is Spatial Polygons Data Frame
  #class(map) (Run for Reference)

#ensure correct averages are associated with correct Region ID
  #map@data (Run for Reference)

#Conversion from SpatialPolygonsDataFrame to DataFrame for manipulation 
#(retaining Data from VWCRegionAv)
map@data$id <- rownames(map@data) #same row names

map@data <- join(map@data, VWCRegionAv, by="Group.1") #associate values by Group.1 (region id)

map.df     <- fortify(map) #conversion to data.frame

map.df     <- join(map.df,map@data) #joins the otherwise lost map@data values to the map.df data frame

 #map.df (Run for Reference) #display data frame

#bounding box method of transpostion 

#define matrix with boundaries of map to box
coordsbox <-  matrix(c(-80.260396, 25.922774,
                  -80.260396, 25.925600,
                 -80.253713, 25.925600,
                  -80.253713, 25.922774,
                  -80.260396, 25.922774), 
                ncol = 2, byrow = TRUE)

#coerce matrix to Polygon object
Polybox <- Polygon(coordsbox)

#coerce Polygon to SpatialPolygons object
SpPolybox <-  SpatialPolygons(list(Polygons(list(Polybox), ID = "1")), proj4string=CRS("+proj=longlat +ellps=WGS84 +datum=WGS84 +no_defs"))

#basic plot of SpatialPolygons object
 #suppressWarnings(plot(SpPolybox, axes = TRUE)) (Run for Reference)

#create utility data.frame in order to create SpatialPolygonsDataFrame
SP.df <- data.frame(ID= 1: length(SpPolybox))

#coerce SpatialPolygons object to SpatialPolygonsDataFrame
SpPolybox.df <- SpatialPolygonsDataFrame(SpPolybox, SP.df)

#create box using border point defined in coordsbox
box <- bbox(SpPolybox.df)

#shows box mins and maxs
box

#creates ggmap of coordsbox boundaries
mapbox <- ggmap(get_map(location = box, maptype = "satellite"))


```

###Forest Measurements Visualization

Below is a map of the forest with red points indicating the position of each measurement recorded during the observation period.

```{r message= FALSE}

#Location of Measurements

Forest_locations <- ggmap(Forest2, extent = "panel") + geom_point(data = SM, aes(x= SM$Lon, y= SM$Lat), lwd= 0.5, color= "red") + 
  ggtitle(" Measurement Locations") + 
  labs(x="Latitude", y="Longitude", caption= "Saint Thomas University, Miami Gardens, FL" )+
  theme(plot.title = element_text(color= "dodgerblue", size = 15, face = "bold", hjust= 0.5), plot.caption = element_text(hjust= 0.5) ,axis.title.x = element_text(color= "sienna1"), axis.title.y = element_text(color= "sienna1")) + commonplot

Forest_locations

#Location of Measurements with grid reference

Grid_Locations <- mapbox +  geom_polygon(data = map.df, aes(x = long, y = lat, group = group), fill= "blue", 
    alpha = 0.04) + coord_map() + geom_point(data = SM, aes(x= SM$Lon, y= SM$Lat), lwd= 0.5, color= "red")+
  xlab("Longitude")+ ylab("Latitude")+theme(
    axis.title.x = element_text(size= 9, color = "orangered"), 
    axis.title.y = element_text(size= 9, color = "orangered"),
    axis.ticks.y = element_blank(), axis.ticks.x = element_blank(), plot.background = element_rect(fill="snow"),
        panel.background = element_rect(fill="white"))+
  geom_path(data = map.df, aes(x = long, y = lat, group = group), color = "white", lwd= 0.07) 

#adds title and subtitle via annotation    
Grid_Locations <- Grid_Locations + annotate("text", x = -80.257, y = 25.9267, label = "Measurement Locations\nOn Region Grid", color= "lightgoldenrod1", size= 5, fontface= "bold")+
  annotate("text", x= -80.25458, y= 25.9215, label= "Saint Thomas University\nMiami Gardens, FL", color= "cornsilk1", size= 2.5)

#plots Grid reference map
Grid_Locations

```

####Soil Moisture Measurement

Volumetric water content percentage (VWC %) was measured over several days in the Saint Thomas University urban forest. The average VWC % value of each determined geographic region was graphed using a choropleth map.

The regions most orange represent grid regions with significant soil aridity. Soil in these regions is mostly fine, white, shallow sand with a great deal of loose limestone rock as well. Little if any vegetation grows in these areas. 

Dark blue grid regions represent areas with more saturated soil. The soil in these regions is brownish sand with a large amount of decomposing organic matter. The soil is also covered with pine needles, leaves, and vines. Most of the surface area in these saturated regions are constantly shielded from the sun by a thick subtropical canopy.

```{r message=FALSE}
#Choropleth grid for example 
Choroplethbase1 <- ggplot(map.df, aes(x=long, y=lat, group=group))+
  geom_polygon(aes(fill=x, alpha= 0.4)) + 
  scale_fill_gradient2(low = "orange", mid = "skyblue",
      high = "blue", midpoint = 3.419, space = "Lab",
      na.value = "grey50", guide = "colourbar")+
  coord_fixed() + guides(alpha= "none")+
  guides(fill=guide_colorbar(title="VWC %\n", order = -1), alpha= "none") + commonplot + ggtitle("Average Soil Volumetric Water\nContent Percentage")+ theme(plot.title = element_text(color="red", face = "bold", hjust=0.5)) + labs(x= "Longitude", y= "Latitude")

Choroplethbase1

#Choropleth map with divergent color scale
Choromap_VWC1 <- mapbox +  geom_polygon(data = map.df, aes(x = long, y = lat, group = group, fill = x), 
    alpha = 0.4) + coord_map() +
  scale_fill_gradient2(low = "orange", mid = "skyblue",
    high = "blue", midpoint = 3.419, space = "Lab",
    na.value = "grey50", guide = "colourbar")+
  guides(fill=guide_colorbar(title="VWC %\n", order = -1), alpha= "none") +
  xlab("Longitude")+ ylab("Latitude")+theme(
    plot.subtitle = element_text(color= "black", hjust = 0.5), 
    legend.title = element_text(color= "orangered", size = 12),
    axis.title.x = element_text(size= 9, color = "orangered"), 
    axis.title.y = element_text(size= 9, color = "orangered"),
    axis.ticks.y = element_blank(), axis.ticks.x = element_blank()) + geom_path(data = map.df, aes(x = long, y = lat, group = group), color = "white", lwd= 0.05) + commonplot

#adds title and subtitle via annotation    
Choromap_VWC1 <- Choromap_VWC1 + annotate("text", x = -80.257, y = 25.9267, label = "Average Soil Volumetric Water\nContent Percentage", color= "lightgoldenrod1", size= 5, fontface= "bold")+
  annotate("text", x= -80.25458, y= 25.9215, label= "Saint Thomas University\nMiami Gardens, FL", color= "cornsilk1", size= 2.5)

#plots Choropleth map with divergent color scale
Choromap_VWC1


#Alternate Choropleth map with continous color scale of blues
Choromap_VWC2 <- mapbox +  geom_polygon(data = map.df, aes(x = long, y = lat, group = group, fill = x), 
      alpha = 0.6) + coord_map() + 
  scale_fill_gradient2(low = "powderblue", mid = "skyblue2",
      high = "slateblue4", midpoint = 3.419, space = "Lab",
      na.value = "grey50", guide = "colourbar")+
  guides(fill=guide_colorbar(title="VWC %\n", order = -1), alpha= "none") +
  xlab("Longitude")+ ylab("Latitude")+theme(
      plot.subtitle = element_text(color= "black", hjust = 0.5), 
      legend.title = element_text(color= "orangered", size = 12),
      axis.title.x = element_text(size= 9, color = "orangered"), 
      axis.title.y = element_text(size= 9, color = "orangered"),
      axis.ticks.y = element_blank(), axis.ticks.x = element_blank())+
  geom_path(data = map.df, aes(x = long, y = lat, group = group), color = "white", lwd= 0.05) + commonplot

#adds title and subtitle via annotation    
Choromap_VWC2 <- Choromap_VWC2 + annotate("text", x = -80.257, y = 25.9267, label = "Average Soil Volumetric Water\nContent Percentage", color= "lightgoldenrod1", size= 5, fontface= "bold")+
  annotate("text", x= -80.25458, y= 25.9215, label= "Saint Thomas University\nMiami Gardens, FL", color= "cornsilk1", size= 2.5)

#plots Alternate Choropleth map
Choromap_VWC2
```


####Choropleth Maps for Other Variables

First, create a new data frame which excludes NA and empty observations for measurements other than VWC. The column SM$UVAIntensity is used because it is the column with the least measurements; ensuring that all empty and NA rows will be removed.

```{r messages= FALSE}
#remove rows with NA or blank measurements by UVAIntensity variable 
#SMO: O stands for measurements other than VWC
SMO <- SM[!(is.na(SM$UVAIntensity) | SM$UVAIntensity==""), ]
```

###Air Temperature in Degrees Fahrenheit Choropleth Map

```{r messages=FALSE}
#Air Temperature Choropleth Map

#group AirTemp measurements by Region "number" identifier 
AirTempRegionAv <- aggregate(SMO$AirTemp, by= list(SMO$Region), FUN=mean)

  #AirTempRegionAv (Run for Reference)

#Creating Data.Frame with AirTemp and geographic polygon values

mapAT <- SpatialPolygonsDataFrame(map, AirTempRegionAv) #makes Spatial Polygons Data Frame with AirTempRegionAv as Data

#ensure class is Spatial Polygons Data Frame
  #class(mapAT) (Run for Reference)

#ensure correct averages are associated with correct Region ID
  #mapAT@data (Run for Reference)

#Conversion from SpatialPolygonsDataFrame to DataFrame for manipulation 
#(retaining Data from VWCRegionAv)
mapAT@data$id <- rownames(mapAT@data) #same row names

mapAT@data <- join(mapAT@data, AirTempRegionAv, by="Group.1") #associate values by Group.1 (region id)

mapAT.df     <- fortify(mapAT) #conversion to data.frame

mapAT.df     <- join(mapAT.df,mapAT@data)

  #mapAT.df (Run for Reference)


#AirTemp Choropleth map with reddish color scale
Choromap_AT <- mapbox +  geom_polygon(data = mapAT.df, aes(x = long, y = lat, group = group, fill = x), 
      alpha = 0.6) + coord_map() +
  scale_fill_gradient(low = "purple",
      high = "orange",
      na.value = "grey50", guide = "colourbar")+
  guides(fill=guide_colorbar(title="°F\n", order = -1), alpha= "none") +
  xlab("Longitude")+ ylab("Latitude")+theme(
    plot.subtitle = element_text(color= "black", hjust = 0.5), 
    legend.title = element_text(color= "orangered", size = 12),
    axis.title.x = element_text(size= 9, color = "orangered"), 
    axis.title.y = element_text(size= 9, color = "orangered"),
    axis.ticks.y = element_blank(), axis.ticks.x = element_blank()) + geom_path(data = map.df, aes(x = long, y = lat, group = group), color = "white", lwd= 0.05) + commonplot

#adds title and subtitle via annotation    
Choromap_AT <- Choromap_AT + annotate("text", x = -80.257, y = 25.9267, label = "Average Air Temperature Fahrenheit", color= "lightgoldenrod1", size= 5, fontface= "bold")+
  annotate("text", x= -80.25458, y= 25.9215, label= "Saint Thomas University\nMiami Gardens, FL", color= "cornsilk1", size= 2.5)

#plots AirTemp Choropleth map
Choromap_AT
```

###Relative Humidity Percentage Choropleth Map

```{r messages= FALSE}
#Relative Humidity Choropleth map

#group RelHumid measurements by Region "number" identifier
RelHumidRegionAv <- aggregate(SMO$RelHumid, by= list(SMO$Region), FUN= mean)

  #RelHumidRegionAv (Run for Reference)

#Creating Data.Frame with RelHumid and geographic polygon values

mapRH <- SpatialPolygonsDataFrame(map, RelHumidRegionAv) #makes Spatial Polygons Data Frame with AirTempRegionAv as Data

#ensure class is Spatial Polygons Data Frame
  #class(mapRH) (Run for Reference)

#ensure correct averages are associated with correct Region ID
  #mapRH@data (Run for Reference)

#Conversion from SpatialPolygonsDataFrame to DataFrame for manipulation 
#(retaining Data from RelHumidRegionAv)
mapRH@data$id <- rownames(mapRH@data) #same row names

mapRH@data <- join(mapRH@data, RelHumidRegionAv, by="Group.1") #associate values by Group.1 (region id)

mapRH.df     <- fortify(mapRH) #conversion to data.frame

mapRH.df     <- join(mapRH.df, mapRH@data)

  #mapRH.df (Run for Reference)


#RelHumid Choropleth map with blues color scale
Choromap_RH <- mapbox +  geom_polygon(data = mapRH.df, aes(x = long, y = lat, group = group, fill = x), 
    alpha = 0.6) + coord_map() +
  scale_fill_gradient(low = "powderblue",
    high = "royalblue4",
    na.value = "grey50", guide = "colourbar")+
  guides(fill=guide_colorbar(title="Relative\nHumidity %\n", order = -1), alpha= "none") +
  xlab("Longitude")+ ylab("Latitude")+theme(
    plot.subtitle = element_text(color= "black", hjust = 0.5), 
    legend.title = element_text(color= "orangered", size = 12),
    axis.title.x = element_text(size= 9, color = "orangered"), 
    axis.title.y = element_text(size= 9, color = "orangered"),
    axis.ticks.y = element_blank(), axis.ticks.x = element_blank()) + geom_path(data = map.df, aes(x = long, y = lat, group = group), color = "white", lwd= 0.05) + commonplot

#adds title and subtitle via annotation    
Choromap_RH <- Choromap_RH + annotate("text", x = -80.257, y = 25.9267, label = "Average Relative\nHumidity Percentage", color= "lightgoldenrod1", size= 5, fontface= "bold")+
  annotate("text", x= -80.25458, y= 25.9215, label= "Saint Thomas University\nMiami Gardens, FL", color= "cornsilk1", size= 2.5)

#plots RelHumid Choropleth map
Choromap_RH
```

###Infrared Intensity Choropleth Map

```{r messages= FALSE}
#IRIntensity Choropleth map

#group IRIntensity measurements by Region "number identifier
IRIntensityRegionAv <- aggregate(SMO$IRIntensity, by= list(SMO$Region), FUN= mean)

  #IRIntensityRegionAv (Run for Reference)

#Creating Data.Frame with AirTemp and geographic polygon values

mapIR <- SpatialPolygonsDataFrame(map, IRIntensityRegionAv) #makes Spatial Polygons Data Frame with AirTempRegionAv as Data

#ensure class is Spatial Polygons Data Frame
  #class(mapIR) (Run for Reference)

#ensure correct averages are associated with correct Region ID
  #mapIR@data (Run for Reference)

#Conversion from SpatialPolygonsDataFrame to DataFrame for manipulation 
#(retaining Data from VWCRegionAv)
mapIR@data$id <- rownames(mapIR@data) #same row names

mapIR@data <- join(mapIR@data, IRIntensityRegionAv, by="Group.1") #associate values by Group.1 (region id)

mapIR.df <- fortify(mapIR) #conversion to data.frame

mapIR.df <- join(mapIR.df, mapIR@data)

  #mapIR.df (Run for Reference)


#IRIntensity Choropleth map with violet to yellow color scale
Choromap_IR <- mapbox +  geom_polygon(data = mapIR.df, aes(x = long, y = lat, group = group, fill = x), 
    alpha = 0.6) + coord_map() +
  scale_fill_gradient(low = "violetred",
    high = "yellow",
    na.value = "grey50", guide = "colourbar")+
  guides(fill=guide_colorbar(title= expression(W/m^{2}) , order = -1), alpha= "none") +
  xlab("Longitude")+ ylab("Latitude")+theme(
    plot.subtitle = element_text(color= "black", hjust = 0.5), 
    legend.title = element_text(color= "orangered", size = 12),
    axis.title.x = element_text(size= 9, color = "orangered"), 
    axis.title.y = element_text(size= 9, color = "orangered"),
    axis.ticks.y = element_blank(), axis.ticks.x = element_blank()) +
  geom_path(data = map.df, aes(x = long, y = lat, group = group), color = "white", lwd= 0.05) + commonplot

#adds title and subtitle via annotation    
Choromap_IR <- Choromap_IR + annotate("text", x = -80.257, y = 25.9267, label = "Solar Infrared Intensity", color= "lightgoldenrod1", size= 5, fontface= "bold")+
  annotate("text", x = -80.257, y = 25.9264, label = "Watts per Square Meter", color= "lightgoldenrod1", fontface = "bold", size = 3.5) +
  annotate("text", x= -80.25458, y= 25.9215, label= "Saint Thomas University\nMiami Gardens, FL", color= "cornsilk1", size= 2.5)

#plots IRIntensity Choropleth map
Choromap_IR
```

###Ultraviolet Spectrum A Light Intensity Choropleth Map

```{r messages= FALSE}
#UVAIntensity Choropleth map

#group UVAIntensity measurements by Region "number" identifier
UVAIntensityRegionAv <- aggregate(SMO$UVAIntensity, by= list(SMO$Region), FUN= mean)

  #UVAIntensityRegionAv (Run for Reference)

#Creating Data.Frame with AirTemp and geographic polygon values

mapUVA <- SpatialPolygonsDataFrame(map, UVAIntensityRegionAv) #makes Spatial Polygons Data Frame with AirTempRegionAv as Data

#ensure class is Spatial Polygons Data Frame
  #class(mapUVA) (Run for Reference)

#ensure correct averages are associated with correct Region ID
  #mapUVA@data (Run for Reference)

#Conversion from SpatialPolygonsDataFrame to DataFrame for manipulation 
#(retaining Data from VWCRegionAv)
mapUVA@data$id <- rownames(mapUVA@data) #same row names

mapUVA@data <- join(mapUVA@data, UVAIntensityRegionAv, by="Group.1") #associate values by Group.1 (region id)

mapUVA.df     <- fortify(mapUVA) #conversion to data.frame

mapUVA.df     <- join(mapUVA.df, mapUVA@data)

  #mapUVA.df (Run for Reference)


#UVAIntensity Choropleth map with violet to yellow color scale
Choromap_UVA <- mapbox +  geom_polygon(data = mapUVA.df, aes(x = long, y = lat, group = group, fill = x), 
    alpha = 0.6) + coord_map() +
  scale_fill_gradient(low = "violetred",
    high = "yellow",
    na.value = "grey50", guide = "colourbar")+
  guides(fill=guide_colorbar(title= "Relative Intensity\n", order = -1), alpha= "none") +
  xlab("Longitude")+ ylab("Latitude")+theme(
    plot.subtitle = element_text(color= "black", hjust = 0.5), 
    legend.title = element_text(color= "orangered", size = 12),
    axis.title.x = element_text(size= 9, color = "orangered"), 
    axis.title.y = element_text(size= 9, color = "orangered"),
    axis.ticks.y = element_blank(), axis.ticks.x = element_blank()) +
  geom_path(data = map.df, aes(x = long, y = lat, group = group), color = "white", lwd= 0.05) + commonplot

#adds title and subtitle via annotation    
Choromap_UVA <- Choromap_UVA + annotate("text", x = -80.257, y = 25.9267, label = "Solar UVA Light Intensity", color= "lightgoldenrod1", size= 5, fontface= "bold")+
  annotate("text", x = -80.257, y = 25.9264, label = "Relative to Sun", color= "lightgoldenrod1", fontface = "bold", size = 3.5) +
  annotate("text", x= -80.25465, y= 25.9215, label= "Saint Thomas University\nMiami Gardens, FL", color= "cornsilk1", size= 2.5)+
  annotate("text", x= -80.2587, y= 25.9215, label= "UVA Wavelength Range (315-400 nm)\nRelative Intensity Range (0 - 10,000)", color="cornsilk1", size= 2.5)

#plots UVAIntensity Choropleth map
Choromap_UVA
```